maps

### 2024-01-24 maps.Rmd
Update maps.Rmd
updated AIS density map

shipList <- dir("D:/AIS/AIS_West", recursive=TRUE, full.names=TRUE, pattern=".rda")

@@

  print(paste0("Completed", substr(i,21,25)))
}
```

@@

#What is area of these grid cells?
st_area(grid)
st_area(AISgrd)
```
Final AIS maps
```{r fig.width=10}
# ggplot
ggplot(AISgrd) + 
  geom_sf(aes(fill = total)) +
  scale_fill_viridis_c() +
  geom_sf(data = west) +
  geom_sf(data = allDrifts_sf)

# tmap
#tm_basemap(leaflet::providers$Esri.WorldTopoMap) +
  tm_shape(AISgrd) + tm_fill(fill = 'total', 
                             col = 'lightgrey', 
                             fill.legend = tm_legend("Ship Counts"),
                             fill.scale = tm_scale_continuous()) + 
  tm_shape(west) + tm_borders(col = "black", 
                              fill = "papayawhip")+
  tm_shape(detsOnly_sf) + tm_dots(size = 0.2, 
                                  legend.show = TRUE) +
  tm_layout(legend.outside = TRUE) +
  tm_grid(alpha = 0.2, 
          col = "grey") +
  tm_scalebar() +
  tm_compass(type = "arrow", 
             position = c(0.05, 0.05), 
             color.light = "blue") +
  tm_add_legend('symbol',
                fill = "black",
                labels = "Whale Detections",
                size = 0.5,
                lwd = 2) +
  tm_place_legends_right(width = 0.2) +
  tm_title("Daily Counts of Unique AIS Vessels")

>>>>

shipList <- dir("D:/AIS/AIS_West", recursive=TRUE, full.names=TRUE, pattern=".rda")
# be sure to remove AIS_grid.rda from this list (shipList[120])

@@

  print(paste0("Completed ", substr(i,21,25)))
}

# shipList contains AIS_grid.rda which does not have MMSI! Will generate an error, but can ignore.
```

@@

#What is area of these grid cells?
st_area(grid)
st_crs(grid)
st_distance(grid)
st_is_longlat(grid)
st_area(AISgrd)

#0.1385641 (area)

```
Final AIS maps
```{r fig.width=10}
# ggplot
ggplot(AISgrd) + 
  geom_sf(aes(fill = total)) +
  scale_fill_viridis_c() +
  geom_sf(data = west) +
  geom_sf(data = allDrifts_sf)

# tmap
#tm_basemap(leaflet::providers$Esri.WorldTopoMap) +
  tm_shape(AISgrd) + tm_fill(col = 'total', style = 'cont', title = "Ship Counts", palette = "Blues") +
  tm_borders(col = 'lightgrey') +
  tm_shape(west) + tm_fill(col = "papayawhip") + tm_borders(col = "black") +
  tm_shape(detsOnly_sf) + tm_dots(size = 0.1, 
                                  legend.show = TRUE) +
  tm_layout(legend.outside = TRUE) +
  tm_grid(alpha = 0.2, 
          col = "grey") +
  tm_scale_bar(position = "center") +
  tm_compass(type = "arrow", 
             position = c(0.05, 0.05), 
             color.light = "blue") +
  tm_add_legend(type = 'symbol',
                col = "black",
                labels = "Whale Detections",
                size = 0.5,
                lwd = 2) +
  tm_layout(main.title = "Daily Counts of Unique AIS Vessels",
            main.title.position = 'left') +
    tmap_style("white")

# Time frame is from 8-6-18 to 12-2-18, duration of drifts in the water.
# Hexagonal cells are 0.4 degrees across (~43 km)
```
Measure cell distance across
```{r}
measure <- function(lon1,lat1,lon2,lat2) {
    R <- 6378.137                                # radius of earth in Km
    dLat <- (lat2-lat1)*pi/180
    dLon <- (lon2-lon1)*pi/180
    a <- sin((dLat/2))^2 + cos(lat1*pi/180)*cos(lat2*pi/180)*(sin(dLon/2))^2
    c <- 2 * atan2(sqrt(a), sqrt(1-a))
    d <- R * c
    return (d)                            # distance in kilometers
}

#AISgrd[25]
measure(-128.4902, 30.02285, -128.8902, 30.25379)

#AISgrd[801]
measure(-118.8902, 30.71567, -119.2902, 30.94661)

#AISgrd[400]
measure(-125.0902, 36.60464, -125.4902, 36.83558)

library(geosphere)
p1 <- c(-128.4902, 30.02285)
p2 <- c(-128.8902, 30.25379)
#distance in meters
distHaversine(p1,p2)
```
